Ensembler: Enabling high-throughput molecular simulations at the superfamily scale

### 2015-03-25 manuscript/ms.tex
Minor

While Modeller's automodel function can generate its own alignments automatically, it was more convenient from a software architecture standpoint to use a standalone function.
As such, we implemented pairwise alignment functionality using the the BioPython {\tt pairwise2} module {\color{red}[CITE: BioPython]}---which uses a dynamic programming algorithm---with the PAM 250 scoring matrix of Gonnet \textit{et al.}~\cite{gonnet:science:1992:exhaustive-matching}.

>>>>

While Modeller's automodel function can generate its own alignments automatically, a standalone function was preferable for reasons of programming convenience.
As such, we implemented pairwise alignment functionality using the the BioPython {\tt pairwise2} module {\color{red}[CITE: BioPython]}---which uses a dynamic programming algorithm---with the PAM 250 scoring matrix of Gonnet \textit{et al.}~\cite{gonnet:science:1992:exhaustive-matching}.
